### 2024-04-02 paper/paper.qmd
Update paper.qmd

---
title: "Analysis Toronto Library"
subtitle: "My subtitle if needed"
author: 
  - Wentao Sun
thanks: "Code and data are available at: https://github.com/TonySun1107/Toronto_library.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-04-17 paper/paper.qmd
Update paper.qmd

@@
 ---
-title: "Analysis Toronto Library"
-subtitle: "My subtitle if needed"
-author: 
-  - Wentao Sun
-thanks: "Code and data are available at: https://github.com/TonySun1107/Toronto_library.git."
+title: "*"
+author: Wentao Sun
+thanks: "Code and data are available at: https://github.com/TonySun1107/Water_Quality.git"
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "*"
 format: pdf
+toc: true
 number-sections: true
@@
 ---
-
 ```{r}
@@
 
+# SET UP WORKSPACE
 library(tidyverse)
-library(palmerpenguins)
+library(dplyr)
+library(here)
+library(modelsummary)
+library(tidyverse)
+library(lubridate)
+library(GGally)
+library(knitr)
+
+```
+\newpage
+# Introduction
+
+As we moved into the 21st century, the growth of industry and technology brought environmental sustainability into focus.
+Water resources of desired quality and quantity are the foundation for human survival and sustainable development [@citehuang2021].
+Sustainable development is development that meets the needs of the present without compromising the ability of future generations to meet their own needs [@citebrundtland1987].
+The concept of sustainable development promotes accurate quantitative analysis and review of the human living environment, culminating in a burgeoning field of water quality research.
+This body of work is crucial in comprehending the nuanced impacts of modern society on natural water systems and in shaping policies for the preservation of these vital resources.
+
+The dissolved oxygen (DO) concentration is a critical parameter for evaluating the ecological health of an aquatic environment [@citehuang2021].
+This concentration results from an equilibrium between oxygen-producing (e.g., photosynthesis and air diffusing) and oxygen-consuming (e.g., aerobic respiration, nitrification, and chemical oxidation) processes in an aquatic environment [@citeolyaie2017].
+In conditions of low dissolved oxygen concentrations prevalent in water bodies receiving heavy sewage pollution [@citeaston1973].
+Combining quantitative data analysis and water quality research, this study investigated dissolved oxygen levels in a bay, a fishing pond, and three other pools to assess water quality in a variety of aquatic environments from 1989 to 2019.Data provided by the U.S.
+Department of the Interior were selected for this study to understand the various measurements of a given body of water, including salinity, ph, and water temperature.
+including salinity, ph, and water temperature.
+The dissolved oxygen of the waters were analyzed in detail using the Corrected Total Oxygen Reading (CTOR).The CTOR value can be used as a quantitative measure of the change in oxygen.The higher the CTOR, the higher the dissolved oxygen content of the waters and the healthier the water quality.The CTOR values are helpful in evaluating the impacts of the environmental policies and the natural variations on the aquatic health.The CTOR values are used to assess the impacts of the environmental policies and natural variations on the aquatic health.
+
+The paper is structured to facilitate a comprehensive understanding of the study and its implications.
+Following Section 1, Section 2 presents the data, detailing the data sources, analytical techniques, and the rationale behind the chosen methods.
+Section 4 discusses the results of the study, describing the trends summarized in the watershed quality data.
+Section 5 provides an in-depth discussion of these results, exploring potential factors influencing measurements, linking them to broader social policy and environmental issues, and providing recommendations for future research in this area.
+
+## Estimand
+
+The focus of this study was to estimate the causal effect of dissolved oxygen content of waters on water quality, with the salinity and pH of the waters being equally worthy of consideration.
+By studying the data obtained from various measurements in five different waters, the aim is to understand the impact of environmental policies and natural changes on aquatic health.
+
+# Data
+
+This section offers an overview of the datasets utilized in the analysis, focusing specifically on water quality indicators.
+The data, sourced from the open-access US data.gov database, encompasses measurements from a bay, a fishing pond, and three watersheds, covering the period from 1989 to 2019.
+The dataset includes detailed records of oxygen content, pH, salinity, and water temperature, each noted with specific dates.
+This comprehensive dataset enables a detailed examination of the temporal changes in water quality over the thirty-year period.
+Additionally, the analysis explores the relationships among oxygen content, pH, salinity, and overall water quality, providing insights into the environmental dynamics affecting these aquatic systems.
+
+## Source and Methodology
+
+The data collection process for this database was meticulously executed by the U.S.
+Department of the Interior (DOI), employing a diverse array of methodologies such as sampling, naturalistic observation, and experimental testing.
+This multi-faceted approach guaranteed a comprehensive and reliable dataset, which facilitates a thorough analysis and understanding of the environmental variables at play.
+Specifically, water quality data for the Refuge, collected bi-weekly by volunteers, includes measures of turbidity, pH, dissolved oxygen (DO), salinity, and temperature.
+Sampling is conducted at designated locations across several water bodies, including the Bay, D-Pool (fishing pond), and C-Pool, B-Pool, and A-Pool.
+This structured and regular data collection strategy provides valuable insights into the temporal dynamics of water quality within these aquatic ecosystems.
+
+The analysis of this paper makes use of the R programming language [@citeR] for statistical computations and visualizing data.
+The tidyverse package [@citetidyverse] is installed to gain access to other importantR packages, including the dplyr package [@citedplyr] used to manipulate and clean data, the readr package [@citereadr] to read and import data, the here package [@citehere]to create a path to specific saved files, the ggplot2 package [@citeggplot2] to create the data visualizations.
+Additionally, the lubridate package [@citelubridate] facilitated date and time manipulation, the kableExtra package [@citekableExtra] enhanced the creation of complex tables, and the GGally package [@citeGGally] provided extended visualization capabilities, particularly for pairwise data exploration.
+The modelsummary package [@citemodelsummary] was utilized for generating comprehensive summary tables.
+These tools collectively underpin the robust analytical framework that supports the findings presented herein.
+
+## Variables
+
+In order to better understand the data and the research process, we have selected the first ten rows of data to detail the research methodology used, explain its relevance and how it contributes to our understanding of the topic.
+Our focus is on salinity, oxygen, ph and air temperature in the selected waters at different times, which gives a comprehensive understanding of how water quality indicators change when different air temperatures are present.
+
+```{r}
+#| label: tbl-display-raw-data
+#| echo: false
+
+#IMPORT CLEANED DATA FROM OUTPUTS FOLDER 
+water_cleaneddata <- read.csv(here::here("data/cleaned_waterquality_data.csv"),
+                  na.strings = c("N/A",""))
+
+water_cleaneddata <- water_cleaneddata |>
+  arrange(year, month) |>
+  select(year, month, Site_Id, Salinity, Oxygen, pH, Air.Temp, Water.Temp)
+
+water_cleaneddata |>
+  slice(1:10) |> 
+  kable(
+    caption = "First Ten Rows of Water Quality from 1990 to 2019",
+    col.names = c("Year", "Month", "Site ID", "Salinity(ppt)", "Oxygen(mg/L)", "PH", "Air.Temp(°F)", "Water.Temp(°C)"),
+    linesep = "",
+    digits = 1,
+    booktabs = TRUE
+  )
+
+#print(water_cleaneddata)
 ```
 
-# Introduction
+table1, built with `kableExtra` [@citekableExtra], 	display the first ten rows for salinity, oxyge, PH, and air temperature of the selected waters.
+This is a more concise table after removing the vacant data, and it shows the statistics of each indicator for waters of different years and months, providing a streamlined view for subsequent analysis and processing.
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
-
-The remainder of this paper is structured as follows. @sec-data....
-
-# Data {#sec-data}
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+## Preliminary Analysis
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: fig-correlation
+#| fig-cap: Correlation Matrix of Water Quality Indicators from 1989 to 2019
 #| echo: false
+#| #| warning: false
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+water_cleaneddata %>%
+  select(!c(Site_Id, year, month)) %>%
+  ggpairs()
+
 ```
 
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+@fig-correlation, bulit with `GGally` [@citeGGally], presents a comprehensive correlation matrix of water quality indicators, encompassing salinity, dissolved oxygen content, pH levels, and air temperature, collated from 1989 to 2019.
+Each plot within the matrix elucidates the pairwise relationships between these critical environmental parameters.
+The diagonal histograms reveal the distribution of individual indicators, where the dissolved oxygen content exhibits a normal distribution, while pH levels display a bimodal distribution.
+The scatter plots below the diagonal illustrate the interaction between variables, with the correlation coefficient denoted for each.
+Noteworthy is the strong negative correlation between air temperature and dissolved oxygen, suggesting a marked decrease in oxygen levels as temperatures rise.
+On the other hand, salinity and pH exhibit a moderately positive correlation.
 
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: fig-year-oxygen
+#| fig-cap: Annual Variability of Dissolved Oxygen Concentrations from 1989 to 2019
 #| echo: false
 #| warning: false
-#| message: false
 
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
+ggplot(water_cleaneddata, aes(factor(year), Oxygen)) +
+  geom_boxplot() +
+  labs(x = "Year", y = "Dissolved Oxygen (mg/L)") + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
 ```
 
-Talk way more about it.
+@fig-year-oxygen displays a visual exploration of dissolved oxygen trends from 1989 to 2019.
+The boxplots demonstrate relatively stable median oxygen levels over the years, with interquartile ranges suggesting consistent variability.
+However, a distinct dip in levels between 1998 and 1999 indicates a significant disruption in oxygen balance, without noticeable recovery in the following years.
+This pattern may reflect specific environmental events impacting the water body's oxygenation.
+
+```{r}
+#| label: fig-month-oxygen
+#| fig-cap: Seasonal Variation in Dissolved Oxygen Concentration by Month from 1989 to 2019
+#| echo: false
+#| warning: false
+
+ggplot(water_cleaneddata,aes(factor(month),Oxygen))+
+  geom_boxplot()+
+  labs(x = "Month", y = "Dissolved Oxygen (mg/L)") +
+  theme(axis.text.x = element_text(angle = 45,
+                                   hjust = 1))
+```
+
+@fig-month-oxygen displays a monthly distribution of dissolved oxygen levels across an aquatic environment, showcasing the seasonal fluctuations within a calendar year.
+The boxplots are arranged to represent each month, revealing both median oxygen concentrations and the spread of values above and below the median—reflected by the interquartile range.
+It is notable that the later months exhibit greater variability, as evidenced by the length of the whiskers and the presence of outliers, which are indicative of sporadic events affecting water oxygenation.
+This visualization captures the cyclical nature of oxygen levels, potentially correlating with temperature changes and biological cycles within the ecosystem.
+
+```{r}
+#| label: fig-siteid-oxygen
+#| fig-cap: Distribution of Dissolved Oxygen Levels Across Sampling Sites from 1989 to 2019
+#| echo: false
+#| warning: false
+
+ggplot(water_cleaneddata,aes(Site_Id,Oxygen))+
+  geom_boxplot()+
+  labs(x = "Site", y = "Dissolved Oxygen (mg/L)") +
+  theme(axis.text.x = element_text(angle = 45,
+                                   hjust = 1))
+```
+
+@fig-siteid-oxygen illustrates the distribution of dissolved oxygen levels across various sites, as represented by boxplots.
+Each boxplot corresponds to a unique site ID, summarizing the central tendency and variability of oxygen measurements at each location.
+The median line within each box denotes the median dissolved oxygen concentration, while the hinges of the box reflect the interquartile range.
+Notably, certain sites exhibit a wider range of values, indicating more variability in oxygen levels, while others display a tighter interquartile range, suggesting more stable conditions.
+Outliers are depicted as individual points outside the whiskers, indicating observations that stand out from the general distribution and may warrant further investigation.
+The sites are labeled along the x-axis, which has been angled for improved readability.
+This figure provides a comparative view of oxygen content variability, a crucial indicator of water quality and aquatic health, among the sampled sites.
+
+## Measurements
+
+In this study, water quality in a variety of aquatic environments was assessed by analyzing dissolved oxygen levels, a key indicator of ecosystem health.
+The dataset used in this study consists of readings collected from multiple sites over a thirty-year period from 1989 through 2019, with measurements recorded every two weeks to capture seasonal and annual trends.
+
+The data were sourced from recognized online databases, ensuring the reliability and accuracy of the records.
+We employed the Corrected Total Oxygen Reading (CTOR).
+The CTOR is derived by dividing the unique oxygen measurements (types) by the square root of twice the total number of all measurements (tokens).
+This approach offers a normalized value, facilitating a valid comparison of oxygen levels across different sites and times.
+It effectively minimizes the influence of data quantity, allowing for a direct assessment of water quality.
+The CTOR values thus serve as a quantitative measure of oxygen variability and are instrumental in evaluating the impacts of environmental policies and natural changes on aquatic health.
 
 # Model
+```{r model, fig.cap="Model Diagnostic Plots", echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=7}
 
-The goal of our modelling strategy is twofold. Firstly,...
+water <-water_cleaneddata %>% 
+  mutate(year_1999 = ifelse(as.numeric(as.character(year)) >= 1999,1,0)) %>% 
+  select(!c(Air.Temp,year)) 
+fit1 <- lm(Oxygen ~ ., data = water)
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+par(mfrow = c(2,2))
+plot(fit1)
 
-## Model set-up
+# water2 <-water_cleaneddata %>% 
+#   mutate(year_1999 = ifelse(as.numeric(as.character(year)) >= 1999,1,0)) %>% 
+#   select(!c(Air.Temp,Water.Depth,year)) 
+# fit1 <- lm(Oxygen ~ ., data = water2)
+# 
+# par(mfrow = c(2,2))
+# plot(fit1)
+# 
+# summary(fit1)
+# anova(fit1 , update(fit1, .~.-Site_Id))
+# anova(fit1 , update(fit1, .~.-month))
+# modelsummary(
+#   list(
+#     "model" = fit1),
+#   fmt = 2,
+#   stars = TRUE
+# )
+```
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+upload
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
+\newpage
 # Results
 
-Our results are summarized in @tbl-modelresults.
+```{r}
+#| label: tbl-ctor
+#| tbl-cap: Summary of Corrected Total Oxygen Reading (CTOR) Across Various Sites and Years
+#| echo: false
+#| warning: false
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
+library(dplyr)
+library(lubridate)
 
-library(rstanarm)
+# Now, you can calculate the CTOR
+water_ctors <- water_cleaneddata %>%
+  group_by(Site_Id, year) %>%
+  summarise(
+    Total_Oxygen = sum(Oxygen, na.rm = TRUE),  # Sum of Oxygen readings for the year
+    Unique_Oxygen_Values = n_distinct(Oxygen),  # Number of unique Oxygen readings for the year
+    Tokens = n(),  # Total number of Oxygen readings for the year
+    CTOR = Unique_Oxygen_Values / (sqrt(2 * Tokens))  # Calculate the CTOR
+  )
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+water_ctors |>
+  slice(1:1) |>
+  kable(
+    col.names = c("Site ID","Year", "Total Oxygen", "Unique Oxygen Values", "Tokens", "CTOR"),
+    linesep = "",
+    digits = 1,
+    booktabs = TRUE
+  )
 ```
@@
 ```{r}
+#| label: fig-ctor
+#| fig-cap: Corrected Total Oxygen Reading (CTOR) from 1989 to 2019
 #| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
 #| warning: false
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
+ctor_plot <- ggplot(water_ctors, aes(x = as.factor(year), y = CTOR, fill = as.factor(Site_Id))) +
+  geom_boxplot() +
+  labs(
+    x = "Year",
+    y = "CTOR Value",
+    fill = "Site ID"
+  ) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_fill_brewer(palette = "Set1") # 使用色盘来区分不同的站点
 
-# Discussion
-
-## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
-
-\newpage
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
+ctor_plot
 ```
@@
 \newpage
+# Discussion
 
+\newpage
 # References

### 2024-04-18 scripts/03-test_data.R
Update 03-test_data.R

@@ -1,15 +1,32 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Test simulated data.
+# Author: Wentao Sun
+# Data: 2 April 2024
+# Contact: went.sun@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Create simulated data.
+# Any other information needed? None.
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Test data ####
+# test 1
+simulated_data$Read_Date |>
+  class() == "character"
+
+# test 2
+simulated_data$Site_Id |>
+  max() == 50
+
+# test 3
+simulated_data$Year |>
+  class() == "integer"
+
+# test 4
+# variable
+num_uniq <-
+  simulated_vocab_data$production |>
+  unique()
+length(num_uniq) == 2

### 2024-04-18 scripts/04-model.R
Update 04-model.R

@@ -1,36 +1,37 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Model.
+# Author: Wentao Sun
+# Data:4 April 2024
+# Contact: went.sun@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Create simulated data.
+# Any other information needed? None.
+
+set.seed(6607)
+
+# Sample 80% of the data indices for training
+train_samp <- sample(seq_len(nrow(water_cleaneddata)), size = floor(0.8 * nrow(water_cleaneddata)))
+
+# Split data into training and testing sets
+train <- water_cleaneddata[train_samp, ]
 
 
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
+train <-water_cleaneddata %>% 
+  mutate(year_1999 = ifelse(as.numeric(as.character(year)) >= 1999,1,0)) %>% 
+  select(!c(Air.Temp,Water.Depth,year))
 
-#### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+# Run a linear model using the transformed year variable and other predictors
+lin_model <- lm(Oxygen ~ Salinity + pH + Depth + Water.Temp + year_1999,
+                data = train)
 
+# Diagnostic plots for the linear model
+par(mfrow = c(2, 2))
+plot(lin_model)
 
 #### Save model ####
 saveRDS(
-  first_model,
+  lin_model,
   file = "models/first_model.rds"
 )
 

### 2024-04-18 paper/datasheet.qmd
update rendered pdf

---
title: "Datasheet for 'Raw_Data_WaterQuality.csv'"
author: Wentao Sun
thanks: "Code and data are available at: https://github.com/TonySun1107/Water_Quality.git"
date: today
date-format: long
abstract: "This data set contains water quality monitoring records at multiple measurement points since 1994. The main measurement parameters include salinity, dissolved oxygen, pH value, transparency, water temperature and air temperature, aiming to monitor and evaluate changes in environmental water quality. The data are obtained through regular sampling and cover a wide range of time spans and locations, providing important long-term data resources for studying water environment health and ecological changes. These data can be used for environmental science research, policy development, and to promote sustainable water resources management."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @US2019datasheet.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - This dataset was created to analyze water quality in the United States. We were unable to find a publicly available dataset in a structured format that contained the water quality criteria values needed for modeling.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - U.S Department of the Interior
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - None
4. *Any other comments?*
    - None

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- This dataset represents a combination of environmental measurement instances, taken at different times and potentially different locations, focusing on water quality metrics. The presence of multiple types of measurements (like water temperature, air temperature, pH, etc.) suggests a detailed tracking of environmental conditions over time. 
2. *How many instances are there in total (of each type, if appropriate)?*
	- One
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset does not contain all possible instances, it is a sample of instances from a larger set. A larger set is the various indicators of water quality. The sample is not representative of the larger collection.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- The original data includes the year, month and day of the time, water salinity, dissolved oxygen, pH, water depth, water temperature and air temperature.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- None
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Data that did not meet the requirements or that seriously did not meet the requirements were processed before the start of the study.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Relationships between individual instances have been clarified, with a direct negative correlation between dissolved oxygen content and temperature in the same waters. An increase in temperature results in a decrease in dissolved oxygen content.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- The data used in this study is already clear and neat and data splitting is not recommended.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- The first step at the beginning of the study for the presence of errors in the dataset is to clean and analyze the obtained dataset.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- Data sets are self-contained, ensuring that these resources exist and remain unchanged over time。
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- The dataset does not contain data that may be considered confidential.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- The data set does not contain the above factors.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- The dataset is age-identified.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- The data set does not contain the above factors.
16. *Any other comments?*
	- None

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data associated with each instance was obtained through measurements by government professionals. These data are not directly observable. Nor are they reported by subjects or indirectly inferred/derived from other data.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The hardware apparatuses or sensors
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- random sampling
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Staff arranged by government departments have been officially paid by the government.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- 1989-2019
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- None
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- Derived from United States Government data
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- None
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- None
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Pass
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- None

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- There has been no preprocessing/cleaning/labeling of the data.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- Pass
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- Pass
4. *Any other comments?*
	- Pass

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- This dataset has not been used for any task before.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- No link, this is data processed out of a government department.
3. *What (other) tasks could the dataset be used for?*
	- Analysis of environmental protection and future sustainable development.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- The composition of the dataset or the way it was collected and pre-processed/cleaned/labeled will not affect future use.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- None
6. *Any other comments?*
	- None

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset will not be distributed to the entity that created it. The dataset exists only on the government website.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed and promoted via a zip archive on the website.
3. *When will the dataset be distributed?*
	- October 29, 2023
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- https://ecos.fws.gov/ServCat/Reference/Profile/117348
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No third party imposes IP-based or other restrictions on the data associated with the instance.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- The dataset will not be subject to any export controls or other regulatory restrictions.
7. *Any other comments?*
	- None

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- U.S. Department of the Interior
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Github: https://github.com/GSA/data.gov.git
3. *Is there an erratum? If so, please provide a link or other access point.*
	- None
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset will be updated with new instances, the frequency of which will be determined by the Department of the Interior.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- This dataset is not related to people.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the dataset will not be maintained, but new data will be generated. There will be a specialized government department responsible for data measurement and statistics.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Others are not allowed to extend/add/build/contribute to the dataset as this data is collected and processed by official government departments and cannot be manipulated by ordinary people.
8. *Any other comments?*
	- None

\newpage

# References

### 2024-04-18 paper/paper.qmd
update rendered pdf

@@
 ---
-title: "*"
+title: "Impact of Water Conditions on Dissolved Oxygen Level"
 author: Wentao Sun
@@
 date-format: long
-abstract: "*"
+abstract: "This study conducts a thorough analysis of various water quality parameters including dissolved oxygen content, water temperature, salinity, and pH levels within aquatic environments.
+The research primarily investigates the impacts of temperature, salinity, and pH on the dissolved oxygen levels, key indicators of water quality, to discern patterns in environmental changes.
+Findings reveal that both temperature and salinity exert a negative influence on dissolved oxygen levels, with increases in these parameters correlating with reductions in oxygen availability.
+The comprehensive water quality analysis deployed in this research elucidates the intricate interactions among critical determinants of aquatic ecosystem health.
+Ultimately, this study enhances our understanding of how different environmental factors influence dissolved oxygen content, offering valuable insights for the management of aquatic ecosystems and advancing environmental sustainability efforts."
 format: pdf
@@
 library(modelsummary)
-library(tidyverse)
 library(lubridate)
@@
 ```
-\newpage
+
 # Introduction
@@
 
-The analysis of this paper makes use of the R programming language [@citeR] for statistical computations and visualizing data.
-The tidyverse package [@citetidyverse] is installed to gain access to other importantR packages, including the dplyr package [@citedplyr] used to manipulate and clean data, the readr package [@citereadr] to read and import data, the here package [@citehere]to create a path to specific saved files, the ggplot2 package [@citeggplot2] to create the data visualizations.
-Additionally, the lubridate package [@citelubridate] facilitated date and time manipulation, the kableExtra package [@citekableExtra] enhanced the creation of complex tables, and the GGally package [@citeGGally] provided extended visualization capabilities, particularly for pairwise data exploration.
-The modelsummary package [@citemodelsummary] was utilized for generating comprehensive summary tables.
+The analysis of this paper makes use of the `R` programming language [@citeR] for statistical computations and visualizing data.
+The `tidyverse` package [@citetidyverse] is installed to gain access to other importantR packages, including the `dplyr` package [@citedplyr] used to manipulate and clean data, the `readr` package [@citereadr] to read and import data, the `here` package [@citehere]to create a path to specific saved files, the `ggplot2` package [@citeggplot2] to create the data visualizations.
+Additionally, the `lubridate` package [@citelubridate] facilitated date and time manipulation, the `kableExtra` package [@citekableExtra] enhanced the creation of complex tables and the `GGally` package [@citeGGally] provided extended visualization capabilities, particularly for pairwise data exploration.
+The `modelsummary` package [@citemodelsummary] was utilized for generating comprehensive summary tables.
 These tools collectively underpin the robust analytical framework that supports the findings presented herein.
@@
 ```
-
 table1, built with `kableExtra` [@citekableExtra], 	display the first ten rows for salinity, oxyge, PH, and air temperature of the selected waters.
@@
 # Model
-```{r model, fig.cap="Model Diagnostic Plots", echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=7}
+
+Since the dependent variable is continuous, a linear model is considered instead of a logistic model.
+As part of the multiple linear regression modeling, we will include as explanatory variables the salinity of the test waters, the ph of the water, the water temperature, and the time of day when the watershed metrics were measured.
+For the analysis in the rest of this section, the dataset is split 80%/20% for training/testing purposes.
+The statistical programming language R [@citeR] is used to run this model and present the findings from it.
+
+Equation \eqref{eq:linm} represents the model used in this paper
+
+\begin{equation}
+Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + \beta_4 X_4 \label{eq:linm} \end{equation}
+
+In Equation \eqref{eq:linm}:
+
+-   $Y$ the dependent variable, is the dissolved oxygen per liter of water.
+-   $\beta_0$ is the coefficient for intercept.
+-   $X_1$ is the covariate of salinity of water.
+-   $X_2$ is the covariate of PH value of water.
+-   $X_3$ is the covariate of temperature of the water.
+-   $X_4$ is the covariate of the year after 1999.
+-   $\beta_1 \beta_2, \beta_3, \beta_4$ are the coefficients of the variables.
+
+The general assumption behind this modeling is that, holding other variables constant, the average oxygen content has decreased on average after 1999 compared to before.
+In addition, Salinity has a negative effect on oxygen content, with an increase in Salinity leading to a decrease in oxygen content, holding other variables constant.
+This may be due to problems such as the destruction of the natural environment such as biological invasions that occurred in 1999, or it may be the result of illegal emissions from anthropogenic chemical plants.
+There may also be a link between changes in temperature and dissolved oxygen content, given that the measurement of dissolved oxygen content is based on the temperature of the water.
+The model therefore attempts to explore whether there is indeed a statistically significant link between the dissolved oxygen content of the waters and the above factors.
+
+```{r fig-model, fig.cap="Model Diagnostic Plots", echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=7}
+#| label: fig-model
+#| fig-cap: Model Diagnostic Plots
+#| echo: false
+#| warning: false
 
@@
   select(!c(Air.Temp,year))
-fit1 <- lm(Oxygen ~ ., data = water)
+lin_model <- lm(Oxygen ~ Salinity + pH + Water.Temp + year_1999, data = water)
 
 par(mfrow = c(2,2))
-plot(fit1)
+plot(lin_model)
 
-# water2 <-water_cleaneddata %>% 
-#   mutate(year_1999 = ifelse(as.numeric(as.character(year)) >= 1999,1,0)) %>% 
-#   select(!c(Air.Temp,Water.Depth,year)) 
-# fit1 <- lm(Oxygen ~ ., data = water2)
-# 
-# par(mfrow = c(2,2))
-# plot(fit1)
-# 
-# summary(fit1)
-# anova(fit1 , update(fit1, .~.-Site_Id))
-# anova(fit1 , update(fit1, .~.-month))
-# modelsummary(
-#   list(
-#     "model" = fit1),
-#   fmt = 2,
-#   stars = TRUE
-# )
+#lin_model <- readRDS(file = "/cloud/project/models/linear_model.rds")
+
 ```
 
-upload
+The diagnostic plots of the model are shown in @fig-model The fitted values vs.
+residuals graph (top-left) shows a roughly horizontal line, which indicated a linear relationship between the dependent and independent variable.
+Ideally, the residuals should be scattered randomly around the horizontal line at zero, with no discernible pattern.
+A clear pattern, as we see with the red line curving, could indicate issues with linearity or equal variance.
 
-\newpage
+Normal Q-Q (Quantile-Quantile) Plot: This plot checks the assumption that the residuals are normally distributed.
+The points should fall approximately along the 45-degree line.
+The figure shows that most of the points fall on the dashed line, but a significant number of points fall on the right tail of the dashed line, indicating that the residuals may not be perfectly normally distributed.
+
+Scale-Location Plot: This plot, similar to the first, is used to check homoscedasticity.
+The vertical spread of the points should be roughly the same across all levels of fitted values.
+If the spread increases or decreases with the fitted values, it suggests non-constant variance.
+The red line is not horizontal; a slope suggests issues with homoscedasticity.
+
+Residuals vs Leverage: This plot helps to identify influential observations that might have a significant impact on the model's predictions.
+Points that stand out from the crowd, especially if they are outside the dashed Cook's distance lines, are worth checking as they might be unduly influencing the model.
+Note that in all four plots above, points 420, 496, and 592 are labeled as possible outliers, indicating that their inclusion would have a significant impact on the linear model.
+
 # Results
+
+## Model Summary
+
+```{r}
+#| label: tbl-model-summary
+#| tbl-cap: Model Summary of Dissolved Oxygen Based on Salinity, PH, Water.Temp and After year 1999
+#| echo: false
+#| warning: false
+
+#Create model summary table
+modelsummary(
+  list(
+    "model" = lin_model),
+  fmt = 2,
+  output = "latex"
+)
+
+```
+
+@tbl-model-summary shows the coefficients for the model predictor variables.
+We are concerned with the upper half of the table because it provides coefficient values representing the intercept and coefficient values representing the factors affecting the dissolved oxygen content of the water.
+The standard errors of the estimated coefficients are also included in parentheses.
+The degree of error in the predictions is shown in @fig-model.
+The time period explored in this model is from 1999 to 2019.
+It is worth noting that we specify the estimated relationship between the independent and dependent variables.
+Therefore, we combine the estimated relationship with the available data to estimate the coefficients of the model.
+
+The coefficient estimates shown in Table @tbl-model-summary for the final model is equivalent to the following, shown in Equation \eqref{eq:fitted}:
+
+\begin{equation}
+\hat{Y_i} = 11.21 - 0.20 X_{1i} + 0.18 X_{2i} - 0.14 X_{3i} - 3.81 X_{4i}
+\label{eq:fitted} \end{equation}
 
@@
 
+@tbl-ctor offers a detailed quantification of the Corrected Total Oxygen Readings (CTOR) for a select year, providing insights into the oxygen variability at different aquatic sites.
+For instance, in 1999, Site A recorded a total oxygen amount of 11.8 units, with 3 unique measurements (indicated by "Unique Oxygen Values"), out of 3 readings (indicated by "Tokens"), resulting in a CTOR value of 1.2.
+Contrastingly, the Bay area in 1990 exhibited a substantially higher oxygen content of 298.4 units, with 21 unique values from 32 readings, culminating in a CTOR of 2.6, indicating a greater diversity in oxygen measurements for that year and site.This could reflect a more dynamic ecosystem or varying water quality management practices.
+
 ```{r}
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  scale_fill_brewer(palette = "Set1") # 使用色盘来区分不同的站点
+  scale_fill_brewer(palette = "Set1")
 
@@
 
-\newpage
+@fig-ctor displays a scatter plot illustrating the distribution of Corrected Total Oxygen Readings (CTOR) from 1989 to 2019 across different sites.
+Each site is represented by a unique color, and the plot points are dispersed along the y-axis to reflect the CTOR value for each year.
+The data points suggest variability in oxygen content over the years, with some sites showing wider fluctuations, evident from the vertical spread of points, while others exhibit a more consistent CTOR value across the observed timeframe.
+It revealing significant inter-annual variability and potential site-specific environmental influences.
+Sites such as the Bay exhibit peaks in oxygen diversity, which could be attributable to factors such as seasonal biological activity or watershed inputs.
+The temporal spread of the data points across the years underscores the importance of continual monitoring to understand the ecological health of these sites.
+
+When synthesizing the data from @tbl-ctor and @fig-ctor, the narrative of water quality over time and across different sites becomes apparent.
+The numerical data in @tbl-ctor, when viewed alongside the trends in @fig-ctor, suggest that oxygen levels, a proxy for water quality, are subject to fluctuations potentially linked to environmental changes or human interventions.
+The Bay area, with its higher CTOR values, might be indicative of a robust and varied aquatic environment, or it could reflect the impact of episodic events that warrant further investigation.
+The integration of these data sources provides a powerful tool for researchers to identify patterns and hypothesize about underlying causes, which can inform future studies and environmental policies.
+
 # Discussion
+
+This study provides a new perspective on water quality improvement and environmental sustainability.
+Quantitative analysis and integration of data confirmed that the amount of dissolved oxygen in water determines water quality.
+By analyzing the data obtained from the U.S.
+Department of the Interior, it provides help and new perspectives for environmental sustainability and social policy making.
+
+## Findings
+
+The findings of this investigation corroborate the proposed hypothesis, delineating a significant association between the Corrected Total Oxygen Reading (CTOR) and aquatic health, notwithstanding some anomalies in the dataset.
+A comparative analysis of oxygen levels across various bodies of water revealed that the bay exhibited markedly higher oxygen content than its counterparts.
+Following closely, the oxygen levels in the fishing pond were also substantial, potentially suggesting an augmentation due to biotic activity.
+Seasonal trends observed over the three-decade span highlight a diminution in dissolved oxygen during the summer months, aligning with typical seasonal patterns.
+A point of particular concern was identified in 1999, where a pronounced decline in CTOR suggested a critical disruption in the water bodies, from which recovery was not observed until the close of the study period in 2019.
+These insights are pivotal in understanding the temporal and fluctuations of water quality and underscore the need for continuous monitoring and preservation of aquatic ecosystems.
+
+## Sustainable Development and Environmental Impacts
+
+Dissolved oxygen (DO) is a crucial indicator of water quality and a cornerstone of aquatic ecosystem health, integral to sustainable development and minimizing environmental impacts.
+Optimal DO levels support diverse aquatic life, aiding in achieving the sustainable management of water resources and the conservation of life below water, as advocated by the United Nations Sustainable Development Goals.
+Diminished DO levels, often caused by pollution from industrial, agricultural, and urban sources, can lead to ecological imbalances, disrupting food chains and impacting fisheries, which are vital for economic and community sustenance.
+Fisheries have rarely been 'sustainable' [@citepauly2002].
+Efforts to sustain or improve DO concentrations are essential in maintaining the integrity of aquatic habitats and ensuring their resilience against environmental disturbances.
+The choice of pollution control instrument is a crucial environmental policy decision [@citegoulder2008].
+Such initiatives include enforcing stringent waste disposal regulations, promoting green infrastructure, and preserving natural water purification systems like wetlands.
+These measures not only enhance DO levels but also contribute to broader environmental benefits, including improved terrestrial biodiversity and public health.
+Effective management of DO is, therefore, a key component of environmental policy, aligning human activities with ecological preservation to foster a sustainable and prosperous future.
+
+## Weaknesses and Future Research Directions
+
+One limitation of our study is that there are unmeasured variables that can affect dissolved oxygen in waters, such as biological invasions or industrial discharges, that are not fully reflected in our analysis.
+Also, although the CTOR formula was used, it does not give a good indication of the potential factors that contribute to good or bad water quality.
+Pollution of waters from chemicals or radioactive substances cannot be well represented in the CTOR.
+These factors may include the fact that this study did not delve into the trace element content of the water and the abundance of organisms in the water.
+
+Future research should aim to further unravel the complex interactions between dissolved oxygen levels and water quality, or alternatively, the data could be obtained by employing more fine-grained measurements for better processing and analysis.
+In addition, measurement of trace element content in water could provide a more detailed understanding of the factors influencing water quality.
+Understanding these factors is essential to fully analyze and understand water quality in the watershed.
 

### 2024-04-19 paper/paper.qmd
Update paper.qmd

@@
 #IMPORT CLEANED DATA FROM OUTPUTS FOLDER 
-water_cleaneddata <- read.csv(here::here("data/cleaned_waterquality_data.csv"),
+water_cleaneddata <- read.csv(here::here("data/cleaned_data/cleaned_waterquality_data.csv"),
                   na.strings = c("N/A",""))
@@
 
-#lin_model <- readRDS(file = "/cloud/project/models/linear_model.rds")
+#lin_model <- readRDS(file = "models/linear_model.rds")
 

### 2024-04-19 paper/paper.qmd
Update paper.qmd

@@
 title: "Impact of Water Conditions on Dissolved Oxygen Level"
+subtitle: "An Analysis of U.S. Water Quality Data From 1989 to 2019"
 author: Wentao Sun
